---
title: "World Happiness Report 2020"
author:
- familyname: Luo
  othernames: Yu
  address: Monash University
  email: yluo0065@student.monash.com
  correspondingauthor: true
  qualifications:  Master
- familyname: Thakker
  othernames: Khushee
  address: Monash University
  email: ktha0021@student.monash.edu
  qualifications: Master
- familyname: Chen
  othernames: Yunqi
  address: Monash University
  email: yche0454@student.monash.edu
  correspondingauthor: true
  qualifications:  Master
organization: the World Bank data base
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
editor_options: 
  chunk_output_type: console
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message=FALSE, 
                      warning=FALSE,
                      fig.width = 6, 
                      fig.height = 4,
                      fig.align="center")
knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")

# Libraries

library(tidyverse)
library(readxl)
library(kableExtra)
library(bookdown)
library(ggplot2)
library(stringr)
library(lubridate)
```


```{r read-data}
# Read the data
WHR20 <- read_excel("Data/WHR20_DataForFigure2.1.xls")
```

\section*{Introduction}

\section*{1 }
```{r}
library("janitor")
library("kableExtra")
library("plotly")
library("countrycode")
library(data.table)
```

```{r}
happiness <- WHR20 %>% 
  select(`Country name`,`Regional indicator`,`Ladder score`,`Logged GDP per capita`,`Social support`,`Healthy life expectancy`,`Freedom to make life choices`,Generosity,`Perceptions of corruption`) %>% 
  mutate(`Happiness Rank` = rank(-`Ladder score`)) %>% 
  rename(`Happiness Score` = `Ladder score`) %>% clean_names()

#happiness rank : the more the ladder score the higher the rank              

```

```{r regiontable}
reg_avg <- happiness %>%
  select(regional_indicator,happiness_score) %>%
  group_by(regional_indicator) %>%
  summarize(Average = mean(happiness_score)) %>% 
  arrange(-Average)

```

```{r}
happiness$iso3 <- countrycode(happiness$country_name, 'country.name', 'iso3c')

happiness[happiness$country_name=="Kosovo","iso3"] <- "XKX"


```

```{r fig.align='center',fig.height=5,fig.width=8}
plot_ly(happiness, x=~regional_indicator,
              y=~happiness_score,
              type="box",
              boxpoints="all",
              color=~regional_indicator,
        text = ~paste("<b>Region:</b> ", regional_indicator,
                      "<br><b>Country:</b> ", country_name,
                      "<br><b>Happiness Score:</b>", happiness_score))%>%
  layout(xaxis=list(showticklabels = FALSE),
         yaxis=list(title="Happiness Score"),
         legend=list(font = (size = 5)),
         margin=list(b = 100),
         title="Box Plot of Happiness Score by Region")
```


*Happiness Score by Region*

We have collected happiness data from World Happiness Report for 2020. It has global happiness that ranks 156 countries by how happy their citizens perceive themselves to be.<br>
We grouped the countries into different regions in the world to observe which region is the happiest.<br>
From the box plot we see that the happiness scores are quite different among these regions. <br>
The group determined that the **“happiest”** countries were located in **Western Europe**, particularly Finland and Denmark.<br>
Meanwhile the **“least happiest”** countries were located in **Sub-Saharan Africa** and **South Asia**. 


\subsection*{1.2 }


\clearpage
\section*{2 }

\subsection*{2.1 }

\clearpage
\section*{3 }

\subsection*{3.1 }

* Compare Top5, Middle5 and Worst5 Countries

```{r include=FALSE}
top5 <- happiness %>% head(5) %>% mutate(Level = "TOP5")
middle5 <- happiness[76:80, ] %>% mutate(Level = "MIDDLE5")
worst5 <- happiness %>% tail(5) %>% mutate(Level = "WORST5")

comparison <- bind_rows(top5, middle5, worst5)

comparison$Level <- as.factor(comparison$Level)
comparison <- transform(comparison, Level = factor(Level, levels = c("TOP5", "MIDDLE5", "WORST5" )))
```

```{r include=FALSE}

data.table(comparison,
          options = list(
            lengthMenu = c(5, 10, 15)
          ),
          caption = 
            htmltools::tags$caption(
              style = 'caption-side: bottom; text-align: center;', 
              htmltools::em('Data table that only includes top5, middle5 and worst5 countries'))
          )

```

```{r include=FALSE}
comparison.score <- comparison %>% rename("Economy GDP" = "logged_gdp_per_capita" , "Social Support" = "social_support" , "Health" = "healthy_life_expectancy", "Freedom" = "freedom_to_make_life_choices", "Corruption" ="perceptions_of_corruption") %>% 
  gather(key = "columns", value = "score", happiness_score:Corruption)

```


```{r  fig.width=10}
comparison.score %>% 
  ggplot(aes(x = Level, y = score, colour = Level, fill = Level)) + 
  geom_boxplot(position=position_dodge(width=1)) + facet_wrap(~columns, scales = "free") 


```

* Analyzing data of Global Happiness Levels in the world,we were able to discover the impact of each different factor in determining “happiness.”
* Factors to determine happiness score of a country are GDP, Freedom to make choices, how less is the corruption, generosity, heath and social support.
* To understand the relations between factors and happiness score we have take data for the top, median and bottom five countries according to ranked scores.
* We observe that the countries with highest happiness score have a better GDP, less corruption, more freedom to make choices, good health ratio, more generosity and receive social support. 


\subsection*{3.2 }

**Happiness Score for Countries**

The WHR calculates how much of the Happiness Index can be explained by the key factors. Add them all up and you should get close to the actual number. <br>

From the below map you can easily spot the happiest country, Finland. <br>
Finland is ranked 1st according to the happiness score it has. It is said one of the reason why Finnish people are so happy is that they do not have to deal with corruption and black money. <br>
Countries such as Afghanistan and South Sudan have least happiness score.

```{r  fig.width=8}

fig <- plot_ly(happiness, type='choropleth', locations= happiness$iso3 , z= happiness$happiness_score, text= ~paste(
                      "<br><b>Country:</b> ", country_name,
                      "<br><b>Happiness rank:</b>", happiness_rank), colorscale="Viridis")

fig <- fig %>% colorbar(title = "Happiness Score" )

fig <- fig %>% layout(
    title = 'World Happiness Map, Year 2020')
fig

```




\clearpage
\section*{References}


