---
title: "World Happiness Report 2020"
author:
- familyname: Luo
  othernames: Yu
  address: Monash University
  email: yluo0065@student.monash.com
  correspondingauthor: true
  qualifications:  Master
- familyname: Thakker
  othernames: Khushee
  address: Monash University
  email: ktha0021@student.monash.edu
  qualifications: Master
- familyname: Chen
  othernames: Yunqi
  address: Monash University
  email: yche0454@student.monash.edu
  correspondingauthor: true
  qualifications:  Master
organization: the World Bank data base
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::html_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
editor_options: 
  chunk_output_type: console
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message=FALSE, 
                      warning=FALSE,
                      fig.width = 6, 
                      fig.height = 4,
                      fig.align="center")
knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")

# Libraries

library(tidyverse)
library(readxl)
library(kableExtra)
library(bookdown)
library(ggplot2)
library(stringr)
library(lubridate)
```


```{r read-data}
# Read the data
WHR20 <- read_excel("Data/WHR20_DataForFigure2.1.xls")
```

\section*{Introduction}

\section*{1 }

\subsection*{1.2 }


\clearpage
\section*{2 }

\subsection*{2.1 }


\subsection*{2.4 Freedom to make life choices }

```{r}
library(plotly)
```

the score of "Freedom to make life choices" from high to low:
```{r}
free_avg <- WHR20 %>%
  group_by(`Regional indicator`) %>% 
  summarise(average = mean(`Freedom to make life choices`)) %>% 
  arrange(desc(average))

  kable(free_avg)
```

"Freedom to make life choices" score greater than 8.0:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Southeast Asia",  "North America and ANZ", "Western Europe", "Latin America and Caribbean")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Freedom to make life choices`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```

"Freedom to make life choices" score between 0.75-0.8:

```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Commonwealth of Independent States", "South Asia", "Central and Eastern Europe", "East Asia")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Freedom to make life choices`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```

"Freedom to make life choices" score lower than 0.75:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Sub-Saharan Africa", "Middle East and North Africa")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Freedom to make life choices`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```



\subsection*{2.5 Generosity }

the score of "Generosity" from high to low:

```{r}
gene_avg  <- WHR20 %>%
  group_by(`Regional indicator`) %>% 
  summarise(average = mean(`Generosity`)) %>% 
  arrange(desc(average))

  kable(gene_avg)
```


Generosity score greater than 0:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("North America and ANZ","South Asia","Western Europe","South Asia","Sub-Saharan Africa")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Generosity`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```

Generosity score lower than 0:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Commonwealth of Independent States","East Asia","Latin America and Caribbean","Middle East and North Africa","Central and Eastern Europe")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Generosity`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```


\subsection*{2.6 Perceptions of corruption }

the score of "Perceptions of corruption" from high to low:

```{r}
perc_avg  <- WHR20 %>%
  group_by(`Regional indicator`) %>% 
  summarise(average = mean(`Perceptions of corruption`)) %>% 
  arrange(desc(average))

  kable(perc_avg)
```

"Perceptions of corruption" score greater than 0.75:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Central and Eastern Europe","Latin America and Caribbean","South Asia","Sub-Saharan Africa","Middle East and North Africa")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Perceptions of corruption`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```

"Perceptions of corruption" score between 0.70-0.75:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Commonwealth of Independent States","Southeast Asia","East Asia")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Perceptions of corruption`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```

"Perceptions of corruption" score lower than 0.70:
```{r}
 WHR20 %>%
  filter(`Regional indicator` %in% c("Western Europe","North America and ANZ")) %>% 
  ggplot(aes(x = `Ladder score`, 
               y = `Perceptions of corruption`)) +
  geom_point() +
  facet_wrap(~`Regional indicator`, nrow = 1)
```


\clearpage
\section*{3 }

\subsection*{3.1 }

\clearpage
\section*{References}


